Assessment of Multi-Axial Stress State effects of Circular Concrete-Filled Steel Tubular Columns under Flexural Loading

### 2018-03-28 Paper7.tex
$(data)

\title{Assessment of Multi-Axial Stress State effects of Circular Concrete-Filled Steel Tubular Columns under Flexural Loading}
\author{Yadong Jiang \and António Silva \and Bledar Kalemia \and José Miguel Castro \and Ricardo Monteiro}

@@

	\section{Multi-axial Stress States of Circular CFST Members}

@@

	\subsection{Previous Studies on Multi-axial Stress State Influence}

@@

		\label{tb-1}
	\end{table}
	\par
	Figure \ref{fig-4} displays the lateral load versus drift ratio plots comparison of three results, namely the tests results, the DP model results with uniaxial material strength and the DP model results with corrected material strength. The four plots on the left column of the figure belong show the response of the CFST specimens with no axial load. It could be found that, with the correction methods given by Inai et al. 2004 \cite{RN30} and Fujimoto et al. 2004 \cite{RN15}, the accuracy of the DP model had been improved, as good agreements are observed between the DP model with corrected material strength and the test results. But regarding the specimens with constant axial loads (plots on the right column), nearly no improvement of the DP model results is found by applying the correction methods, by comparing its results with the original DP model predictions. As constant factors were used to correct the steel stress in the correction methods given by the two research works, it could be summarized that the steel bi-axial stress state has a relationship with the axial load level.
	\par
	\begin{figure}[h]
		\centering
		\includegraphics[height=0.9\textheight]{Figures/Figure_5.pdf}
		\caption{Lateral load versus drift ratio plots comparison between the test results, the two DP models}
		\label{fig-4}
	\end{figure}
	\par
	\section{Material Strength Correction Methods}
	As concluded in Section 2, the material strength correction methods proposed by previous researchers are not efficient enough to improve the prediction results of the DP model, especially in the cases that the circular CFST members are loaded with lateral force combined with a constant axial load. Thus, new material strength correction methods should be proposed to account for the influence of the multi-axial stress states on the material strength variance of the circular CFST member. Given that the developed 3D FE model (Jiang et al. 2018 [?]) can accurately represent the flexural behaviour of CFST members, this model is used to calibrate this strength correction methodology. In the following paragraphs, the material strength correction methods, which aims to acquire the confined concrete strength ($f_{cc}$) and the steel bi-axial yield stress ($f_{yb}$) from the numerical results given by the 3D FE model, are detailed.
	\par

@@

	\subsection{Yield Points of the Concrete and Steel Sections}

@@

	\subsection{Strength Correction Equations for Concrete}

@@

	\subsection{Strength Correction Equations for Steel}

>>>>

\title{Assessment of Multi-Axial Stress State effects of Circular Concrete-Filled Steel Tubular Columns under Flexural Loading}
\author{Yadong Jiang \and António Silva \and Bledar Kalemia \and José Miguel Castro \and Ricardo Monteiro \and Nuno Silvestre}

@@

	\section{Influence of Multi-axial Stress States}

@@

	\subsection{Previous Studies on Multi-axial Stress State}

@@

		\label{tb-1}
	\end{table}
	\par
	Figure \ref{fig-4} displays the lateral load versus drift ratio plots comparison of three results, namely the tests results, the DP model results with uniaxial material strength and the DP model results with corrected material strength. The four plots on the left column of the figure belong show the response of the CFST specimens with no axial load. It could be found that, with the correction methods given by Inai et al. 2004 \cite{RN30} and Fujimoto et al. 2004 \cite{RN15}, the accuracy of the DP model had been improved, as good agreements are observed between the DP model with corrected material strength and the test results. But regarding the specimens with constant axial loads (plots on the right column), nearly no improvement of the DP model results is found by applying the correction methods, by comparing its results with the original DP model predictions. As constant factors were used to correct the steel stress in the correction methods given by the two research works, it could be summarized that the steel bi-axial stress state has a relationship with the axial load level, which is not considered in the aforementioned correction methods.
	\par
	\begin{figure}[h]
		\centering
		\includegraphics[height=0.9\textheight]{Figures/Figure_5.pdf}
		\caption{Lateral load versus drift ratio plots comparison between the test results, the two DP models}
		\label{fig-4}
	\end{figure}
	\par
	\section{Material Strength Correction Methods}
	As concluded in Section 2, the material strength correction methods proposed by previous researchers are not efficient enough to improve the prediction results of the DP model, especially in the cases that the circular CFST members are loaded with lateral force combined with a constant axial load. Thus, new material strength correction methods should be proposed to account for the influence of the multi-axial stress states on the material strength variance of the circular CFST member. Given that the developed 3D FE model (Jiang et al. 2018 [?]) can accurately represent the flexural behaviour of CFST members, this model is used to calibrate this strength correction methodology. In the following paragraphs, the material strength correction methods, which aims to acquire the confined concrete strength ($f_{cc}$) and the steel bi-axial yield stress ($f_{yb}$) from the numerical results given by the 3D FE model, are detailed.
	\par

@@

	\subsection{Yield Points of Concrete and Steel Sections}

@@

	\subsection{Strength Correction Equation for Concrete}

@@

	\subsection{Strength Correction Equation for Steel}
